### 2022-03-04 paper/localpsf.tex
add back some details to RBF section

\subsubsection{Radial basis function interpolation}

@@

where $b_i$ are radial basis functions and $w_i$ are weights. The vector of weights, $w = (w_1, w_2, \dots, w_k)^T$, is found as the solution to the $k \times k$ linear system

@@

\subsubsection{Improvement for symmetric operators}
\label{sec:symmetric_improvements}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by performing the same interpolation as before, but with $x$ and $y$ taking opposite roles. We combine both of these interpolation schemes to improve the approximation accuracy at negligible additional cost. The two interpolation schemes are combined by placing function values 
\begin{equation*}
\left(\widehat{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widehat{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and using radial basis functions to interpolate the combination of these $2k$ points and values at zero.

>>>>

%\subsubsection{Radial basis function interpolation}

@@

Here $b_i$ are radial basis functions and $w_i$ are weights. The vector of weights, $w = (w_1, w_2, \dots, w_k)^T$, is found as the solution to the $k \times k$ linear system

@@

\subsubsection{Improvement for symmetric operators}
\label{sec:symmetric_improvements}
If $\Aop$ is symmetric, impulse responses of $\Aop$ are also impulse responses of $\Aop^T$. Let $\{y_i\}_{i=1}^k$ be the $k$ nearest sample points to $y$, excluding points $y_i$ such that $x - \mu(y) + \mu(y_i) \notin \Omega$. We could form an alternative approximation of $\Phi(y,x)$ by performing the same interpolation as before, but with $x$ and $y$ taking opposite roles. Both of these interpolation schemes can be combined to improve the approximation accuracy at negligible additional cost. We combine these interpolation schemes by placing function values 
\begin{equation*}
\left(\widehat{f}_x\right)_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $x_i-x$, placing function values
\begin{equation*}
\left(\widehat{f}_y\right)_i := \frac{V(y)}{V(y_i)}\phi_{y_i}\left(x - \mu(y) + \mu(y_i)\right), \qquad i=1,\dots,k,
\end{equation*}
at the points $y_i-y$, and interpolating the combination of these $2k$ points and values at zero.
